Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2021-01-15 manuscript/ERL_global_C_review.Rmd
a bit of cleanup

Despite the importance of forests, comprehensive global studies have historically been limited by the scattered and more local nature of research studies. 
Primary research articles typically cover only a small numbers of sites at a time.
The rare exceptions that span regions or continents with rare exceptions spanning regions or continents are typically coordinated through research networks such as ForestGEO [@anderson-teixeira_ctfs-forestgeo_2015; e.g., @lutz_global_2018], NEON [@schimel_neon_2007], or FLUXNET [@baldocchi_fluxnet_2001; e.g., @novick_ameriflux_2018].
The result of decades of research on forest C cycling is that tens of thousands of records have been distributed across literally thousands of scientific articles --often behind paywalls-- along with variation in data formats, units, measurement methods, *etc.*
In this format, the data are effectively inaccessible for many global-scale analyses, including those attempting to benchmark model performance with global data (Clark et al 2017, Luo et al 2012), quantify the the role of forests in the global C cycle [*e.g.*, @pan_large_2011], or use book-keeping methods to quantify actual or scenario-based exchanges of CO~2~ between forests and the atmosphere [@griscom_natural_2017; @houghton_terrestrial_2020].

To address the need for global-scale analyses of forest C cycling, we recently developed *ForC* [@anderson-teixeira_carbon_2016; @anderson-teixeira_forc_2018].
*ForC* contains published estimates of forest ecosystem C stocks and annual fluxes (>50 variables), with the different variables capturing the unique ecosystem pools (e.g., woody, foliage, and root biomass; dead wood) and flux types (e.g, gross and net primary productivity; soil, root, and ecosystem respiration). 
These data are ground-based measurements, and *ForC* contains associated data required for interpretation (*e.g.*, stand history, measurement methods).
Data have been amalgamated from original peer-reviewed publications, either directly or via intermediary data compilations.
Since the its most recent publication [@anderson-teixeira_forc_2018], *ForC* has grown to include two additional large databases: the Global Soil Respiration Database [SRDB; @bond-lamberty_global_2010] and the Global Reforestation Opportunity Assessment database [GROA; @cook-patton_mapping_2020] that also synthesized published forest C data.
Following these additions, *ForC* currently contains `r nrow(ForC_measurements)` records from `r nrow(ForC_plots)` plots and `r n_areas` distinct geographic areas representing all forested biogeographic and climate zones.
This represents an `r round((nrow(ForC_measurements) - 17367)/17367*100, digits=0)`% increase in records from the prior publication [@anderson-teixeira_forc_2018].

@@

  knitr::include_graphics(paste0(path_to_ForC, "figures/C_cycle_diagrams/Diagrams/Tropical broadleaf MATURE.jpeg"))
```

@@

  knitr::include_graphics(paste0(path_to_ForC, "figures/C_cycle_diagrams/Diagrams/Temperate broadleaf MATURE.jpeg"))
```

@@

  knitr::include_graphics(paste0(path_to_ForC, "figures/C_cycle_diagrams/Diagrams/Temperate conifer MATURE.jpeg"))
```

@@

  knitr::include_graphics(paste0(path_to_ForC, "figures/C_cycle_diagrams/Diagrams/Boreal conifer MATURE.jpeg"))
```
\elandscape

@@

The most notable exception to the pattern of decreasing flux from tropical to boreal biomes was $NEP$, with no significant differences across biomes but with the largest average in temperate broadleaf forests, followed by tropical, boreal, and temperate conifer forests (Figs. `r flux_age_trends`, `rNEP_fig`).

@@

  knitr::include_graphics(paste0(path_to_ForC, "figures/age_trends/for_ERL_review/Flux_age_trends.jpeg"))
```

@@

  knitr::include_graphics(paste0(path_to_ForC, "figures/age_trends/for_ERL_review/Stock_age_trends.jpeg"))
```

>>>>

Despite the importance of forests, comprehensive global studies have historically been limited by the scattered and more local nature of research studies. 
Primary research articles typically cover only a small numbers of sites at a time.
The rare exceptions spanning regions or continents are typically coordinated through research networks such as ForestGEO [@anderson-teixeira_ctfs-forestgeo_2015; e.g., @lutz_global_2018], NEON [@schimel_neon_2007], or FLUXNET [@baldocchi_fluxnet_2001; e.g., @novick_ameriflux_2018].
The result of decades of research on forest C cycling is that tens of thousands of records have been distributed across literally thousands of scientific articles --often behind paywalls-- along with variation in data formats, units, measurement methods, *etc.*
In this format, the data are effectively inaccessible for many global-scale analyses, including those attempting to benchmark model performance with global data (Clark et al 2017, Luo et al 2012), quantify the the role of forests in the global C cycle [*e.g.*, @pan_large_2011], or use book-keeping methods to quantify actual or scenario-based exchanges of CO~2~ between forests and the atmosphere [@griscom_natural_2017; @houghton_terrestrial_2020].

To address the need for global-scale analyses of forest C cycling, we recently developed *ForC* [@anderson-teixeira_carbon_2016; @anderson-teixeira_forc_2018].
*ForC* contains published estimates of forest ecosystem C stocks and annual fluxes (>50 variables), with the different variables capturing the unique ecosystem pools (e.g., woody, foliage, and root biomass; dead wood) and flux types (e.g, gross and net primary productivity; soil, root, and ecosystem respiration). 
These data are ground-based measurements, and *ForC* contains associated data required for interpretation (*e.g.*, stand history, measurement methods).
Data have been amalgamated from original peer-reviewed publications, either directly or via intermediary data compilations.
Since its most recent publication [@anderson-teixeira_forc_2018], *ForC* has grown to include two additional large databases: the Global Soil Respiration Database [SRDB; @bond-lamberty_global_2010] and the Global Reforestation Opportunity Assessment database [GROA; @cook-patton_mapping_2020] that also synthesized published forest C data.
Following these additions, *ForC* currently contains `r nrow(ForC_measurements)` records from `r nrow(ForC_plots)` plots and `r n_areas` distinct geographic areas representing all forested biogeographic and climate zones.
This represents an `r round((nrow(ForC_measurements) - 17367)/17367*100, digits=0)`% increase in records from the prior publication [@anderson-teixeira_forc_2018].

@@

  knitr::include_graphics("tables_figures/C_cycle_diagrams/Tropical_broadleaf_MATURE.jpeg")
```

@@

  knitr::include_graphics("tables_figures/C_cycle_diagrams/Temperate_broadleaf_MATURE.jpeg")
```

@@

  knitr::include_graphics("tables_figures/C_cycle_diagrams/Temperate_conifer_MATURE.jpeg")
```

@@

  knitr::include_graphics("tables_figures/C_cycle_diagrams/Boreal_conifer_MATURE.jpeg")
```
\elandscape

@@

The most notable exception to the pattern of decreasing flux per unit area from tropical to boreal biomes was $NEP$, with no significant differences across biomes but with the largest average in temperate broadleaf forests, followed by tropical, boreal, and temperate conifer forests (Figs. `r flux_age_trends`, `rNEP_fig`).

@@

  knitr::include_graphics("tables_figures/age_trends/for_ERL_review/Flux_age_trends.jpeg")
```

@@

  knitr::include_graphics("tables_figures//age_trends/for_ERL_review/Stock_age_trends.jpeg")
```
